Moving Together

### 2023-01-26 graphs_newt_snakes/Same_V.Rmd
small sim to community for slim 4 and some edits to other files

@@

What does it mean to be correlated?

@@

>>>>

Run four sets of simulations each with 16 different genetic architectures (GA), to explore how changing mutation rate and the standard deviation of mutation effect size can impact how traits coevolve. Each GA within a simulation set will have the same mutational variance.

@@

What does it mean to be correlated and can I get spatial phenotypic correlation when populations of newts and snakes are coevolving?

@@

V = 2.5e^-13:

- mu = 1e^-8 sig = 0.005
- mu = 1e^-9 sig = 0.0158
- mu = 1e^-10 sig = 0.05
- mu = 1e^-11 sig = 0.158

V = 2.5e^-12:

- mu = 1e^-8 sig = 0.0158
- mu = 1e^-9 sig = 0.05
- mu = 1e^-10 sig = 0.158
- mu = 1e^-11 sig = 0.5

V = 2.5e^-11:

- mu = 1e^-8 sig = 0.05
- mu = 1e^-9 sig = 0.158
- mu = 1e^-10 sig = 0.5
- mu = 1e^-11 sig = 1.58

V = 2.5e^-10:

- mu = 1e^-8 sig = 0.158
- mu = 1e^-9 sig = 0.5
- mu = 1e^-10 sig = 1.58
- mu = 1e^-11 sig = 5.0

### 2023-01-26 graphs_newt_snakes/high_to_low_v.Rmd
small sim to community for slim 4 and some edits to other files

@@

What does it mean to be correlated?

@@

>>>>

I ran 4 simulation sets, where in each set the mutation rate stayed constant and I changed the mutation effect size to create varying levels of mutational variance.

@@

What does it mean to be correlated? How much of an advantage is an increase in mutational variance for a species involved in an coevolutionary race?

@@

mu = 1e^-8:

 - sig = 0.005, MV = 2.5e^-13
 - sig = 0.0158, MV = 2.5e^-12
 - sig = 0.05, MV = 2.5e^-11
 - sig = 0.158, MV = 2.5e^-10

 mu = 1e^-9:

 - sig = 0.0158, MV = 2.5e^-13
 - sig = 0.05, MV = 2.5e^-12
 - sig = 0.158, MV = 2.5e^-11
 - sig = 0.5, MV = 2.5e^-10

 mu = 1e^-10:

 - sig = 0.05, MV = 2.5e^-13
 - sig = 0.158, MV = 2.5e^-12
 - sig = 0.5, MV = 2.5e^-11
 - sig = 1.58, MV = 2.5e^-10

 mu = 1e^-11:

 - sig = 0.158, MV = 2.5e^-13
 - sig = 0.5, MV = 2.5e^-12
 - sig = 1.58, MV = 2.5e^-11
 - sig = 5.0, MV = 2.5e^-10

### 2023-01-26 graphs_newt_snakes/move_together.Rmd
small sim to community for slim 4 and some edits to other files

@@

What does it mean to be correlated? Might this occur if I simulatate some controlled movement?

@@

@@

genend_newt = aggregate(move_together_lit[which(move_together_lit$generation>=move_together_lit$Nstr_gen  & move_together_lit$Newt_mean_Pheno>=(move_together_lit$Nend)) ,]$generation, list(move_together_lit[which( move_together_lit$generation>=move_together_lit$Nstr_gen  & move_together_lit$Newt_mean_Pheno>=(move_together_lit$Nend)),]$group_rep), FUN=min)

genend_snake = aggregate(move_together_lit[which(move_together_lit$generation>=move_together_lit$Sstr_gen  & move_together_lit$Snake_mean_Pheno>=(move_together_lit$Send)) ,]$generation, list(move_together_lit[which(move_together_lit$generation>=move_together_lit$Sstr_gen  & move_together_lit$Snake_mean_Pheno>=(move_together_lit$Send)),]$group_rep), FUN=min)

@@

@@

```{r, making newts and snakes in grid form}

@@

main_plot<-ggplot(data_long_type_comp, aes(x = x_loc, y = y_loc))+
  geom_tile(aes(fill = as.numeric(measurement)))+
  facet_wrap(~species)+

  theme_bw()+
  theme(legend.justification = "top")

@@

final_plot <- main_plot +  inset_element(extra_plot, left = 1., bottom = -0.10, right = 1.35, top = 0.5)

@@

>>>>

Start populations in the lower third of the simulation and let them move as they co-evolve. It is possible that as newts and snakes move into new territory they might create more spatial phenotype correlation.

@@

What does it mean to be correlated? Might this occur if I simulate some controlled movement?

@@

I am running a coevolution experiment where newts and snakes interaction with each other over long periods of time. When they interact the newt or snake with the highest level of toxicity or resistance will survive. As newts and snake interact across space, they develop exaggerated traits that can become spatial correlated. My experiments examine when traits became exaggerated or correlated.

@@

genend_newt = aggregate(move_together_lit[which(move_together_lit$generation>=move_together_lit$Nstr_gen  & move_together_lit$Newt_mean_Pheno>=(.98*(move_together_lit$Nend))) ,]$generation, list(move_together_lit[which( move_together_lit$generation>=move_together_lit$Nstr_gen  & move_together_lit$Newt_mean_Pheno>=(.98*move_together_lit$Nend)),]$group_rep), FUN=min)

genend_snake = aggregate(move_together_lit[which(move_together_lit$generation>=move_together_lit$Sstr_gen  & move_together_lit$Snake_mean_Pheno>=(.98*move_together_lit$Send)) ,]$generation, list(move_together_lit[which(move_together_lit$generation>=move_together_lit$Sstr_gen  & move_together_lit$Snake_mean_Pheno>=(.98*move_together_lit$Send)),]$group_rep), FUN=min)

@@

npt<-ggplot(move_together_lit) +
geom_boxplot(aes(sim, genend_newt), color="darkred")
spt<-ggplot(move_together_lit) +
geom_boxplot(aes(sim, genend_snake), color="steelblue")
#  geom_point(aes(group_rep, genend_newt), color="darkred")+
 # geom_point(aes(group_rep, genend_snake), color="steelblue")
grid.arrange(npt, spt, ncol=1)
ggplot(move_together_lit) +
  facet_wrap(~sim)+
geom_point(aes(rep, genend_newt), color="darkred")+
geom_point(aes(rep, genend_snake), color="steelblue")

ggplot(move_together_lit) +
geom_boxplot(aes(sim, genend_snake-genend_newt), color="black")

@@

```{r, making newts and snakes in grid form look nice}

@@

main_plot<-ggplot(data_long_type_comp, aes(x = x_loc, y = y_loc))+
  geom_tile(aes(fill = as.numeric(measurement)))+
  facet_wrap(~species)+
  coord_fixed() +
  theme_bw()+
  #margin(t = 0, r = 0, b = 0, l = 0, unit = "pt")+
  theme( legend.justification = "top", 
         plot.margin = margin(t = 0.3,  # Top margin
                             r = 0,  # Right margin
                             b = 0.3,  # Bottom margin
                             l = 0,  # Left margin
                             unit = "cm")  ) # legend.position ="bottom"
#plot.margin = unit(c(1, 1, 3, 1), "cm"),
if(type != "num_ind"){
  main_plot<- main_plot + labs(title = paste0(str_to_title(type)," Phenotype of Locations"),
                               subtitle = paste0(file_name, ", Generation: ", spegen),
                               fill = "Toxicity/Resistance")+
    scale_fill_viridis_c()
}
if(type == "num_ind"){
  main_plot<- main_plot + labs(title = paste0("Number of Individuals at Locations ", str_to_title(type)),
                               subtitle = paste0(file_name, ", Generation: ", spegen),
                               fill = "Newt/Snake PopSize")+
    scale_fill_viridis_c(option = "plasma")
}

@@

bloan <- ggplot() + theme_void()
final_plot <- grid.arrange(main_plot, arrangeGrob(bloan, extra_plot), ncol = 2)

grid.arrange(main_plot, bloan, extra_plot, ncol = 2, 
             layout_matrix=cbind(c(1,1),c(2,3)))

#final_plot <- main_plot +  inset_element(extra_plot, left = 1., bottom = -0.10, right = 1.35, top = 0.5)

@@

duo_grid_plot(file_name, spegen, file, type, row_num, col_num)
```

```{r, looking at the slop}

file = move_together_lit
title = "test"
subt = "test"
x_label ="xx"
y_label = "yy"
min_gen = 100
max_gen = 50000

  ggplot(file[ which(file$generation>=min_gen & file$generation<=max_gen),]) +
    facet_wrap(~sim)+
    #geom_line(aes(generation, dif, group=rep, col="dif"))+
    ggtitle(title, subtitle = paste0(subt, " From ", min_gen, " gen to ", max_gen, " gen")) +
    geom_line(aes(generation, Snake_mean_Pheno, group=rep, color="Snake_mean_Pheno"),)+
    geom_line(aes(generation, Newt_mean_Pheno, group=rep, color="Newt_mean_Pheno"))+
    #geom_hline(yintercept=0, linetype="dashed", color="gray54")+
    #coord_trans(y="log2")+
    scale_y_continuous(trans = "log2")+
    #ylim(-1.,2.5)+
    xlab(x_label) + ylab(y_label)+
    scale_color_manual(name = "Type",
values = c( "Snake_mean_Pheno" = "steelblue", "Newt_mean_Pheno" = "darkred", "dif" = "black"),
labels = c("Snake", "Newt", "Dif"))+
    theme_bw() + theme(axis.text.x = element_text(angle = 45, hjust=1, size = 8), legend.position="none",
                      strip.background = element_blank(), strip.text.x = element_blank(),
                      title =element_text(size=8, face='bold'), axis.title.x = element_blank(),
                      axis.title.y = element_blank())
